Subjective Experience of Demands and Resources across O*NET Job Elements

### 2024-07-11 Submission.Rmd
enable line numbers
added second correlation table

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : yes
draft             : no

@@

@@

cr_eng_m1 <- lm(scale(engagement) ~ scale(overall.challenge_center), modreg)
#summary(cr_eng_m1)

cr_eng_m2 <- lm(scale(engagement) ~ scale(overall.challenge_center) + scale(overall.resource_center), modreg)
#summary(cr_eng_m2)

cr_eng_m3 <- lm(scale(engagement) ~ scale(overall.challenge_center) + scale(overall.resource_center) + scale(overall.challenge_center*overall.resource_center), modreg)
#summary(cr_eng_m3)

@@

hr_burn_m1 <- lm(scale(burnout) ~ scale(overall.hindrance_center), modreg)
#summary(hr_burn_m1)

hr_burn_m2 <- lm(scale(burnout) ~ scale(overall.hindrance_center) + scale(overall.resource_center), modreg)
#summary(hr_burn_m2)

hr_burn_m3 <- lm(scale(burnout) ~ scale(overall.hindrance_center) + scale(overall.resource_center) + scale(overall.hindrance_center*overall.resource_center), modreg)
#summary(hr_burn_m3)

@@

hr_stress_m1 <- lm(scale(stress) ~ scale(overall.hindrance_center), modreg)
#summary(hr_stress_m1)

hr_stress_m2 <- lm(scale(stress) ~ scale(overall.hindrance_center) + scale(overall.resource_center), modreg)
#summary(hr_stress_m2)

hr_stress_m3 <- lm(scale(stress) ~ scale(overall.hindrance_center) + scale(overall.resource_center) + scale(overall.hindrance_center*overall.resource_center), modreg)
#summary(hr_stress_m3)

@@

hr_eng_m1 <- lm(scale(engagement) ~ scale(overall.hindrance_center), modreg)
#summary(hr_eng_m1)

hr_eng_m2 <- lm(scale(engagement) ~ scale(overall.hindrance_center) + scale(overall.resource_center), modreg)
#summary(hr_eng_m2)

hr_eng_m3 <- lm(scale(engagement) ~ scale(overall.hindrance_center) + scale(overall.resource_center) + scale(overall.hindrance_center*overall.resource_center), modreg)
#summary(hr_eng_m3)

@@

DV <- c("Engagement","","", "Stress","","", "Burnout","","")
Step <- c("1", "","2", "1", "","2", "1", "","2")
Model <- c("Challenge", "Resource", "Challenge X Resource", "Challenge", "Resource", "Challenge X Resource", "Challenge", "Resource", "Challenge X Resource")
Beta <- c(sigfill(chal.2.eng), paste(res.2.eng,"**"), paste(int.cr.3.eng,"*"), chal.2.stress, res.2.stress, int.cr.3.stress, paste(chal.2.burn,"**"), res.2.burn, int.cr.3.burn)
R2 <- c("", paste(cr_eng_m2_r,"**"), paste(cr_eng_m3_r,"**"), "", round(cr_stress_m2_r,2), round(cr_stress_m3_r,2), "", paste(round(cr_burn_m2_r,2),"**"), paste(round(cr_burn_m3_r,2),"**"))
DeltaR <- c("","", paste(cr_eng_r_square_change,"*"), "","",cr_stress_r_square_change, "","",cr_burn_r_square_change)

>>>>

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : yes
draft             : no

@@

names(data_new)[names(data_new) == "engagement"] <- "Engagement"
names(data_new)[names(data_new) == "burnout"] <- "Burnout"

r_second <- corx::corx(data_new, x =c("Challenge", "Hindrance", "Resource", "Stress", "Burnout", "Engagement"),                          triangle = "lower",
                stars = c(0.05, 0.01, 0.001),
                describe = c(`$M$` = mean, `$SD$` = sd))

papaja::apa_table(r_second$apa, 
                  caption = "Overall variable bivariate correlations.",
                  escape = FALSE, 
                  note = "$*$ p < .05, $**$ p < .01, $***$ p < .001")
```

@@

cr_eng_m1 <- lm((engagement) ~ scale(overall.challenge_center), modreg)
#summary(cr_eng_m1)

cr_eng_m2 <- lm((engagement) ~ scale(overall.challenge_center) + scale(overall.resource_center), modreg)
#summary(cr_eng_m2)

cr_eng_m3 <- lm((engagement) ~ scale(overall.challenge_center) + scale(overall.resource_center) + scale(overall.challenge_center*overall.resource_center), modreg)
#summary(cr_eng_m3)

@@

hr_burn_m1 <- lm((burnout) ~ scale(overall.hindrance_center), modreg)
#summary(hr_burn_m1)

hr_burn_m2 <- lm((burnout) ~ scale(overall.hindrance_center) + scale(overall.resource_center), modreg)
#summary(hr_burn_m2)

hr_burn_m3 <- lm((burnout) ~ scale(overall.hindrance_center) + scale(overall.resource_center) + scale(overall.hindrance_center*overall.resource_center), modreg)
#summary(hr_burn_m3)

@@

hr_stress_m1 <- lm((stress) ~ scale(overall.hindrance_center), modreg)
#summary(hr_stress_m1)

hr_stress_m2 <- lm((stress) ~ scale(overall.hindrance_center) + scale(overall.resource_center), modreg)
#summary(hr_stress_m2)

hr_stress_m3 <- lm((stress) ~ scale(overall.hindrance_center) + scale(overall.resource_center) + scale(overall.hindrance_center*overall.resource_center), modreg)
#summary(hr_stress_m3)

@@

hr_eng_m1 <- lm((engagement) ~ scale(overall.hindrance_center), modreg)
#summary(hr_eng_m1)

hr_eng_m2 <- lm((engagement) ~ scale(overall.hindrance_center) + scale(overall.resource_center), modreg)
#summary(hr_eng_m2)

hr_eng_m3 <- lm((engagement) ~ scale(overall.hindrance_center) + scale(overall.resource_center) + scale(overall.hindrance_center*overall.resource_center), modreg)
#summary(hr_eng_m3)

@@

DV <- c("Engagement","","", "Stress","","", "Burnout","","")
Step <- c("1", "","2", "1", "","2", "1", "","2")
Model <- c("Challenge", "Resource", "Challenge", "Resource", "Challenge X Resource", "Challenge", "Resource", "Challenge", "Resource", "Challenge X Resource", "Challenge", "Resource", "Challenge", "Resource", "Challenge X Resource")
Beta <- c(sigfill(chal.2.eng), paste(res.2.eng,"**"), paste(int.cr.3.eng,"*"), chal.2.stress, res.2.stress, int.cr.3.stress, paste(chal.2.burn,"**"), res.2.burn, int.cr.3.burn)
R2 <- c("", paste(cr_eng_m2_r,"**"), paste(cr_eng_m3_r,"**"), "", round(cr_stress_m2_r,2), round(cr_stress_m3_r,2), "", paste(round(cr_burn_m2_r,2),"**"), paste(round(cr_burn_m3_r,2),"**"))
DeltaR <- c("","", paste(cr_eng_r_square_change,"*"), "","",cr_stress_r_square_change, "","",cr_burn_r_square_change)

### 2024-07-11 Submission.tex
enable line numbers
added second correlation table

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{O*Net, challenge-hindrance framework, job demands-resources, job characteristics\newline\indent Word count: 4,942}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{csquotes}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={Subjective Experience of Demands and Resources across O*NET Job Elements},
  pdflang={en-EN},
  pdfkeywords={O*Net, challenge-hindrance framework, job demands-resources, job characteristics},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

@@

@@

\begin{tabular}{llllll}
\toprule
DV & \multicolumn{1}{c}{Step} & \multicolumn{1}{c}{Model} & \multicolumn{1}{c}{$\beta$} & \multicolumn{1}{c}{$R^2$} & \multicolumn{1}{c}{$\Delta R^2$}\\
\midrule
Engagement & 1 & Challenge & -0.10 &  & \\
 &  & Resource & 0.48 ** & 0.15 ** & \\
 & 2 & Challenge X Resource & -0.09 * & 0.16 ** & 0.01 *\\
Stress & 1 & Challenge & 0.14 &  & \\
 &  & Resource & -0.07 & 0.01 & \\
 & 2 & Challenge X Resource & 0.02 & 0.01 & 0.00\\
Burnout & 1 & Challenge & 0.33 ** &  & \\
 &  & Resource & -0.14 & 0.04 ** & \\
 & 2 & Challenge X Resource & 0.06 & 0.04 ** & 0.00\\
\bottomrule
\addlinespace
\end{tabular}

@@

\begin{tabular}{llllll}
\toprule
DV & \multicolumn{1}{c}{Step} & \multicolumn{1}{c}{Model} & \multicolumn{1}{c}{$\beta$} & \multicolumn{1}{c}{$R^2$} & \multicolumn{1}{c}{$\Delta R^2$}\\
\midrule
Engagement & 1 & Hindrance & -0.14 ** &  & \\
 &  & Resource & 0.46 ** & 0.17 ** & \\
 & 2 & Hindrance X Resource & -0.02 & 0.17 ** & 0.00\\
Stress & 1 & Hindrance & 0.10 * &  & \\
 &  & Resource & 0.02 ** & 0.01 * & \\
 & 2 & Hindrance X Resource & -0.19 ** & 0.04 ** & 0.03 **\\
Burnout & 1 & Hindrance & 0.10 * &  & \\
 &  & Resource & 0.12 * & 0.04 ** & \\
 & 2 & Hindrance X Resource & -0.13 ** & 0.05 ** & 0.01 **\\
\bottomrule
\addlinespace
\end{tabular}

>>>>

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{O*Net, challenge-hindrance framework, job demands-resources, job characteristics\newline\indent Word count: 4,942}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{lineno}

\linenumbers
\usepackage{csquotes}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={Subjective Experience of Demands and Resources across O*NET Job Elements},
  pdflang={en-EN},
  pdfkeywords={O*Net, challenge-hindrance framework, job demands-resources, job characteristics},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

@@

\caption{\label{tab:unnamed-chunk-1}Overall variable bivariate correlations.}

\begin{tabular}{llllllll}
\toprule
 & \multicolumn{1}{c}{1} & \multicolumn{1}{c}{2} & \multicolumn{1}{c}{3} & \multicolumn{1}{c}{4} & \multicolumn{1}{c}{5} & \multicolumn{1}{c}{$M$} & \multicolumn{1}{c}{$SD$}\\
\midrule
1. Challenge & - &  &  &  &  & 3.75 & 0.50\\
2. Hindrance & -.21*** & - &  &  &  & 2.39 & 0.78\\
3. Resource & .74*** & -.25*** & - &  &  & 3.77 & 0.48\\
4. Stress & -.03 & .11** & -.08 & - &  & 2.59 & 0.97\\
5. Burnout & -.05 & .08 & -.08 & .70*** & - & 3.04 & 0.87\\
6. Engagement & .28*** & -.11** & .33*** & -.24*** & -.30*** & 4.03 & 0.79\\
\bottomrule
\addlinespace
\end{tabular}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} $*$ p < .05, $**$ p < .01, $***$ p < .001}
\end{tablenotes}

@@

\begin{tabular}{llllll}
\toprule
DV & \multicolumn{1}{c}{Step} & \multicolumn{1}{c}{Model} & \multicolumn{1}{c}{$\beta$} & \multicolumn{1}{c}{$R^2$} & \multicolumn{1}{c}{$\Delta R^2$}\\
\midrule
Engagement & 1 & Challenge & -0.08 &  & \\
 &  & Resource & 0.37 ** & 0.15 ** & \\
 & 2 & Challenge & -0.07 * & 0.16 ** & 0.01 *\\
Stress & 1 & Resource & 0.14 &  & \\
 &  & Challenge X Resource & -0.07 & 0.01 & \\
 & 2 & Challenge & 0.02 & 0.01 & 0.00\\
Burnout & 1 & Resource & 0.33 ** &  & \\
 &  & Challenge & -0.14 & 0.04 ** & \\
 & 2 & Resource & 0.06 & 0.04 ** & 0.00\\
Engagement & 1 & Challenge X Resource & -0.08 &  & \\
 &  & Challenge & 0.37 ** & 0.15 ** & \\
 & 2 & Resource & -0.07 * & 0.16 ** & 0.01 *\\
Stress & 1 & Challenge & 0.14 &  & \\
 &  & Resource & -0.07 & 0.01 & \\
 & 2 & Challenge X Resource & 0.02 & 0.01 & 0.00\\
\bottomrule
\addlinespace
\end{tabular}

@@

\begin{tabular}{llllll}
\toprule
DV & \multicolumn{1}{c}{Step} & \multicolumn{1}{c}{Model} & \multicolumn{1}{c}{$\beta$} & \multicolumn{1}{c}{$R^2$} & \multicolumn{1}{c}{$\Delta R^2$}\\
\midrule
Engagement & 1 & Hindrance & -0.11 ** &  & \\
 &  & Resource & 0.35 ** & 0.17 ** & \\
 & 2 & Hindrance X Resource & -0.01 & 0.17 ** & 0.00\\
Stress & 1 & Hindrance & 0.08 * &  & \\
 &  & Resource & 0.01 ** & 0.01 * & \\
 & 2 & Hindrance X Resource & -0.17 ** & 0.04 ** & 0.03 **\\
Burnout & 1 & Hindrance & 0.09 * &  & \\
 &  & Resource & 0.1 * & 0.04 ** & \\
 & 2 & Hindrance X Resource & -0.11 ** & 0.05 ** & 0.01 **\\
\bottomrule
\addlinespace
\end{tabular}
